A Survey of Quantitative Descriptions of Molecular Structure

### 2012-04-09 paper.tex
Done with desc versioning section

\subsection{Descriptor Versioning}
\label{sec:descr-vers}

@@

>>>>

\subsection{Descriptor Naming \& Versioning}
\label{sec:descr-vers}

@@

A topic closely related to versioning is descriptor naming. The
preceding sections have discussed a categorization of descriptors and
have used a number of commonly used names. When performing
calculations in an automated manner, or employing remote services for
descriptor calculations \cite{Dong:2007aa}, it is useful to be able to
refer to descriptors via a standardized naming scheme. Currently the
QSAR modeling community lacks such a scheme, though the Chemistry
Developmen Kit (CDK), a Java library for cheminformatics
\cite{Steinbeck:2006aa} does implement such a scheme. The ``descriptor
specification'' approach defines a set of classes that include
information of the implementation title, identifier and vendor. The
identifier may or may not incude a version number. The actual details
of the a descriptor are listed in a dictionary, along with an optional
namespace. The dictionary entry is referenced by the descriptor
specification and this design thus allows one to seamlessly work with
multiple implementations of the same descriptor from different vendors
and keep track of which version is employed throughout a calculation
or workflow. In addition, the CDK provides a hierarchical annotation
of descriptors, grouping them into different classes. Since this
annotation is based on RDF \cite{Taylor:2006ab}, it allows one to go
beyond simple groupings and perform reasoning on descriptors. A simple
example is to identify functionally equivalent descriptors (such as
simple transformations of a base descriptor - square and cube roots of
the gravitational index is an example \cite{Wessel:1998ve}) in an
automated fashion. While this infrastructure is currently only
supported by the CDK, adoption of it (or some similar framework) would
enable easier interoperability between descriptor implementations and
enhance reproducibility.
